Data Processing

### 2020-01-24 analysis/data_processing.Rmd
update visualizations

data <- read_csv("../data/data.csv")%>%
  mutate(subage = factor(subage),
         trial = ifelse(test_day == "2", trial + 4, trial))%>%
  select(-X)

@@

ggplot(data = p12, aes(x = age, y = mean))+
  geom_hline(yintercept = .5, lty = 2)+
  geom_jitter(alpha = .5, width = .2, height = .01)+
  geom_smooth(method = "glm")+
  facet_grid(~task)+
  labs(x = "Age", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))+
  coord_fixed(ratio = 2)
```
# Card Sorting model

@@

card_sorting_model_data <- card_sorting_data %>%
  mutate(age = age - mean(age),
         trial = trial - mean(trial))

# card_sorting_model1 <- brm(correct ~ age + trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model1.rds")
# 
# card_sorting_model2 <- brm(correct ~ trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model2.rds")

@@

ts <- loo_compare(card_sorting_model1, card_sorting_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, card_sorting_model1 = "correct ~ age + trial + RE", 
                   card_sorting_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

ts

@@

```{r}
p_sum_cs1 <- card_sorting_data %>%
  mutate(subage = as.numeric(as.character(subage)))%>%
  group_by(age,subage,id) %>%
  summarise(correct = mean(correct))

p_sum_cs2 <- p_sum_cs1 %>%
  group_by(subage) %>%
  multi_boot_standard(col = "correct")

samples_cs_1 <- posterior_samples(card_sorting_model1, "^b")%>%
  mutate(sample = 1:length(b_age))

samples_cs_2 <- expand_grid(samples_cs_1,card_sorting_model_data$age)%>%
  mutate(y = plogis(b_Intercept + b_age * `card_sorting_model_data$age`),
         age = `card_sorting_model_data$age` + mean(card_sorting_data$age),
         experiment = "card_sorting")%>%
  filter(sample < 1000)

map_cs <- tibble(
  age = card_sorting_model_data$age,
  int = fixef(card_sorting_model1)[1,1],
  slope = fixef(card_sorting_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(card_sorting_data$age_num))

p_cs <- ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples_cs_2, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = map_cs, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_sum_cs1,aes(x = age, y= correct), width = .00, height = .01, alpha = .5)+
  geom_pointrange(data = p_sum_cs2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .2), pch = 4)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  scale_color_manual(values = "#CC6677")
```

>>>>

data <- read_csv("../data/data.csv")%>%
  mutate(subage = factor(subage),
         trial = ifelse(test_day == "2", trial + 4, trial),
         z_age = age - mean(age))%>%
  select(-X)

@@

ggplot(data = p12, aes(x = age, y = mean))+
  geom_hline(yintercept = .5, lty = 2)+
  geom_jitter(alpha = .5, width = .2, height = .01)+
  geom_smooth(method = "glm")+
  facet_grid(~task)+
  labs(x = "Age", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  theme_few()+
  theme(legend.position = c(.85,.2))+
  coord_fixed(ratio = 2)
```
# Models

## Card Sorting

@@

card_sorting_model_data <- card_sorting_data %>%
  mutate(trial = trial - mean(trial))

# card_sorting_model1 <- brm(correct ~ z_age + trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model1.rds")
# 
# card_sorting_model2 <- brm(correct ~ trial + (trial|id),
#                     data = card_sorting_model_data, family = bernoulli(),
#           control = list(adapt_delta = 0.99),
#           sample_prior = F,
#           chains = 4, 
#           cores = 4,
#           save_all_pars = TRUE,
#           iter = 10000)%>%
#   add_criterion("waic")%>%
#   saveRDS(., "../saves/card_sorting_model2.rds")

@@

cs_ts <- loo_compare(card_sorting_model1, card_sorting_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, card_sorting_model1 = "correct ~ age + trial + RE", 
                   card_sorting_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

cs_ts

@@

## Inforamtiveness

```{r}

inf_data <- data %>%
  filter(task == "informativeness")

inf_model_data <- inf_data %>%
  mutate(trial = trial - mean(trial))

inf_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = inf_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/inf_model1.rds")

inf_model2 <- brm(correct ~ trial + (trial|id),
                    data = inf_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/inf_model2.rds")

inf_model1 <-readRDS("../saves/inf_model1.rds")

inf_model2 <-readRDS("../saves/inf_model2.rds")

inf_ts <- loo_compare(inf_model1, inf_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, inf_model1 = "correct ~ age + trial + RE", 
                   inf_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

inf_ts

summary(inf_data_model1)

## Mutual Exclusivity

```{r}

me_data <- data %>%
  filter(task == "mutual_exclusivity")

me_model_data <- me_data %>%
  mutate(trial = trial - mean(trial))

me_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = me_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/me_model1.rds")

me_model2 <- brm(correct ~ trial + (trial|id),
                    data = me_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/me_model2.rds")

me_model1 <-readRDS("../saves/me_model1.rds")

me_model2 <-readRDS("../saves/me_model2.rds")

me_ts <- loo_compare(me_model1, me_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, me_model1 = "correct ~ age + trial + RE", 
                   me_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

me_ts

summary(me_model1)

```
## Novelty

```{r}

nov_data <- data %>%
  filter(task == "novelty")

nov_model_data <- nov_data %>%
  mutate(trial = trial - mean(trial))

nov_model1 <- brm(correct ~ z_age + trial + (trial|id),
                    data = nov_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/nov_model1.rds")

nov_model2 <- brm(correct ~ trial + (trial|id),
                    data = nov_model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          chains = 4,
          cores = 4,
          save_all_pars = TRUE,
          iter = 10000)%>%
  add_criterion("waic")%>%
  saveRDS(., "../saves/nov_model2.rds")

nov_model1 <-readRDS("../saves/nov_model1.rds")

nov_model2 <-readRDS("../saves/nov_model2.rds")

nov_ts <- loo_compare(nov_model1, nov_model2, criterion = "waic")%>%
  as.data.frame() %>%
  tibble::rownames_to_column("Model")%>%
  mutate(
    Model = recode(Model, nov_model1 = "correct ~ age + trial + RE", 
                   nov_model2 = "correct ~ trial + RE"),
    weight = exp(elpd_waic) / sum(exp(elpd_waic)),
    weight = round(weight, 3),
    WAIC = round(waic, 2),
    SE = round(se_waic,2))%>%
  select(Model, WAIC, SE, weight)

nov_ts

summary(nov_model1)

```
# Visualizing individual tasks

```{r}
# Files to plot data means
p_data <- data %>%
  filter(task != "training")%>%
  mutate(subage = as.numeric(as.character(subage)))%>%
  group_by(task, age,subage,id) %>%
  summarise(correct = mean(correct))

p_data2 <- p_data %>%
  group_by(task, subage) %>%
  multi_boot_standard(col = "correct")

# Files to plot individual samples from each task
samples_to_draw <- sample(1:20000, 500)

## card sorting
samples_cs <- posterior_samples(card_sorting_model1, "^b")%>%
  mutate(sample = 1:length(b_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "card_sorting")

## informativeness
samples_inf <- posterior_samples(inf_model1, "^b")%>%
  mutate(sample = 1:length(b_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "informativeness")

## mutual exclusivity
samples_me <- posterior_samples(me_model1, "^b")%>%
  mutate(sample = 1:length(b_z_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "mutual_exclusivity")
## novelty

samples_nov <- posterior_samples(nov_model1, "^b")%>%
  mutate(sample = 1:length(b_z_age))%>%
  filter(sample %in% samples_to_draw)%>%
  expand_grid(data$z_age)%>%
  mutate(y = plogis(b_Intercept + b_z_age * `data$z_age`),
         age = `data$z_age` + mean(data$age),
         task = "novelty")

## combine files
samples <- bind_rows(
  samples_cs,
  samples_inf,
  samples_me,
  samples_nov
)

# File to plot means of distributions for each task

## card sorting
map_cs <- tibble(
  age = data$z_age,
  int = fixef(card_sorting_model1)[1,1],
  slope = fixef(card_sorting_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(data$age),
         task = "card_sorting")

## informativeness
map_inf <- tibble(
  age = data$z_age,
  int = fixef(inf_model1)[1,1],
  slope = fixef(inf_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(data$age),
         task = "informativeness")

## mutual exclusivity
map_me <- tibble(
  age = data$z_age,
  int = fixef(me_model1)[1,1],
  slope = fixef(me_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(data$age),
         task = "mutual_exclusivity")

## novelty
map_nov <- tibble(
  age = data$z_age,
  int = fixef(nov_model1)[1,1],
  slope = fixef(nov_model1)[2,1]
)%>%
  mutate(y = plogis(int + slope * age),
         age = age + mean(data$age),
         task = "novelty")

maps <- bind_rows(
  map_cs,
  map_inf,
  map_me,
  map_nov
)

ggplot() +
  geom_hline(yintercept = .5, lty=2, size = 1)+
  geom_line(data = samples, aes(x = age, y = y, group = sample), size = .025, col = "grey")+
  geom_line(data = maps, aes(x = age, y = y), size = 1)+
  geom_jitter(data = p_data,aes(x = age, y= correct), width = .00, height = .01, alpha = .2)+
  geom_pointrange(data = p_data2, aes(x = subage+.5, y = mean, ymin = ci_lower, ymax = ci_upper),size = .5, position = position_dodge(width = .2), pch = 5, col = "#6866cc")+
  labs(x="Age",y="Proportion correct")+
  facet_wrap(~task, nrow = 2)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F, col = F)+
  coord_fixed(ratio = 2)
```
